Introduction

### 2015-07-15 dissertation/introdefhistory.tex
add labels
fix ref title

\section{Overview}

@@

\section{Semantic Web -- A definition?}

@@

\section{A personal history}

@@

At this point, I left Opera to work as a consultant on Semantic Web
technologies. One of the projects that were successfully completed was
called Sublima\cite{TODO}. It was driven entirely by RDF and SPARQL,
and featured faceted navigation, navigation in a thesaurus, and full
text search. Experiences from this project influenced requirements of
SPARQL 1.1, and I was an editor of the SPARQL 1.1 Features and
Requirements specification\cite{TODO}. Parts of the property paths
feature and aggregate queries were used extensively. Write operations
were also implemented with SPARQL using what was then specified only
in a member submission to the W3C\cite{TODO}. This was the basis for
the update language in SPARQL 1.1 but differed substantially in
surface syntax, partly because our work showed how certain patterns
could be simplified.

>>>>

\section{Overview}\label{sec:introoverview}

@@

\section{Semantic Web -- A definition?}\label{sec:noref}

@@

\section{A personal history}\label{sec:history}

@@

At this point, I left Opera to work as a consultant on Semantic Web
technologies. One of the projects that were successfully completed was
called Sublima\cite{TODO}. It was driven entirely by RDF and SPARQL,
and featured faceted navigation, navigation in a thesaurus, and full
text search. Experiences from this project influenced requirements of
SPARQL 1.1, and I was an editor of the SPARQL 1.1 Features and
Rationale specification\cite{TODO}. Parts of the property paths
feature and aggregate queries were used extensively. Write operations
were also implemented with SPARQL using what was then specified only
in a member submission to the W3C\cite{TODO}. This was the basis for
the update language in SPARQL 1.1 but differed substantially in
surface syntax, partly because our work showed how certain patterns
could be simplified.
